<h1 align="center" style="color:blue">Exploring Corruption Policies outcomes worlwide</h1>

By: **StudentA**, **StudentB** and **StudentC**
<br>
<br>

______

Our group is interested in corruption. This is how corruption is behaving worldwide:

```{r}
dataLink="https://github.com/EvansDataScience/basicFinal_VISUAL/raw/master/dataProject.csv"
df=read.csv(dataLink,stringsAsFactors = FALSE)
```

These are the contents:

```{r}
str(df)
```

## Univariate plots:

```{r}
summary(df$corruption)
```

The variable corruption measures how well countrues are facing it. Then, 75% of the countries achieve at most a score of 57. No country achieves a score greater than 90.

You can see the distribution here:

```{r}
hist(df$corruption)
```

That plot does not allow to find if we have outliers, for that we need a boxplot:

```{r}
boxplot(df$corruption,horizontal = TRUE)
```


## Bivariate plots:

Let me see the median of corruption by continent:

```{r}
boxplot(df$corruption~df$Continent,horizontal = TRUE,las=2)
```


Let me see how each of the proposed predictors  relates to our dependent variable:

```{r}
plot(df$corruption,df$press)
```

```{r}
plot(df$corruption,df$economy)
```

We know that the predictors have a fairly linear relationship with the dependent variable, then we can test our hypothesis by seeing the effect of each controlling by the other: 

```{r}
test=lm(as.numeric(corruption)~press+economy,data=df)
```

The result is shown here:
```{r}
summary(test)
```

As we see above, our model is **significant** with a decent Adjusted R-squared:
```{r}
summary(test)$adj.r.squared
```

Next, we need to verify some requisites so that our results are trustable.

1. The residuals should seems normally distributed: for that we need to see them along the vertical of the qqplot.

```{r}
# normality of residuals?
library(car)
qqPlot(test, main="QQ Plot")
```

2. The error variance changes with the level of the response, which will happen if the output of the _ncvTest_ function is non-significant.

```{r}
# homocedastic?
ncvTest(test)
```

3. The predictors are no highly correlated:

```{r}
# collinearity?
vif(test) > 4 # problem?
```

4. Detect the change if influential observations are eliminated:
```{r}
influencePlot(test, id.method = 'noteworthy', main="Influence Plot", sub="Circle size is proportial to Cook's Distance" )
```

Those cases (rows) are not considered now:

```{r}
CountrysOUT=c(122,149)
summary(lm(as.numeric(corruption)~press+economy,
           data=df[-CountrysOUT,]))
```

As you can see, this got better...


______

[GO BACK TO REPO](https://github.com/EvansDataScience/basicFinal_CompThink)