<h1 align="center" style="color:blue">Exploring Corruption Policies outcomes worlwide</h1>

By: **StudentA**, **StudentB** and **StudentC**
<br>
<br>

______

Our group is interested in corruption. This is how corruption is behaving worldwide:

```{r}
dataLink="https://github.com/EvansDataScience/basicFinal_VISUAL/raw/master/dataProject.csv"
df=read.csv(dataLink,stringsAsFactors = FALSE)
```

These are the contents:

```{r}
str(df)
```

## Univariate plots:

```{r}
summary(df$corruption)
```

The variable corruption measures how well countrues are facing it. Then, 75% of the countries achieve at most a score of 57. No country achieves a score greater than 90.

You can see the distribution here:

```{r}
hist(df$corruption)
```

That plot does not allow to find if we have outliers, for that we need a boxplot:

```{r}
boxplot(df$corruption,horizontal = TRUE)
```


## Bivariate plots:

Let me see the median of corruption by continent:

```{r}
boxplot(df$corruption~df$Continent,horizontal = FALSE,las=2)
```

The total did not detect outliers, but the bivariate exploration  did. Let's see if those median values are statistically different:

```{r nonparam, eval=FALSE}
# non parametric
kruskal.test(corruption~factor(Continent), data = df)
```


We should wonder what variables could explain this variability worldwide. 

Let me see how each of the proposed predictors  relates to our dependent variable:

```{r}
plot(df$corruption,df$press)
```

```{r}
plot(df$corruption,df$economy)
```


## Multivariate plots:


We know that the predictors have a fairly linear relationship with the dependent variable, then we can test our hypothesis by seeing the effect of each controlling by the other: 

```{r}
test=lm(as.numeric(corruption)~press+economy,data=df)
```

The result is shown here:
```{r}
summary(test)
```

A helpful plot will help us show the effect of those predictors on corruption.


```{r}
library(dotwhisker)
library(broom)
library(dplyr)
```

There is some preprocessing needed to use ggplot. 

```{r}
model1_t = tidy(test) %>%   
    mutate(model = "Model 1")

dwplot(model1_t) + 
    geom_vline(xintercept = 0, 
               colour = "grey60", 
               linetype = 2) +
    scale_colour_grey(start = .1, end = .7) +theme_bw()
```

We have seen that all these variables are well related. We could try a cluster analysis, let me try four clusters:

```{r}
library(cluster)
set.seed(123)

# computing clusters
result <- kmeans(df[,c(3:5)],
                 centers = 5)

df$cluster=as.factor(result$cluster)
```

Let's see the median of each cluster:
```{r}
boxplot(df$corruption~df$cluster,horizontal = FALSE,las=2)
```

We should recode the las two clusters:

```{r, eval=TRUE}
library(car)
df$cluster<-car::recode(df$cluster,"4=5;5=4")
```

And see how the world looks like.

Let me show you the map:

```{r, eval=TRUE}
library(rgdal)
folder='world_map'
file='world_map.shp'
mapFile=file.path(folder,file)

#original map
mapWorld = rgdal::readOGR(mapFile,stringsAsFactors=F) 
```

The _mapWorld_ file has the following columns:
```{r}
names(mapWorld)
```

Then, we can merge that file with our current data frame:

```{r, eval=TRUE}

# NEW map
mapWorldAll=merge(mapWorld, #map first
                   df, 
                   by.x='ISO3', # common column
                   by.y='iso', # common column
                   all.x=F) # reduced map.
```

Now paint the world:

```{r, eval=TRUE}
# what:
varToPlot=mapWorldAll$cluster

#which colors: (order of clusters)

palette = c('black','green','yellow','orange','magenta')

# plotting:

## base layer (original map)
plot(mapWorld,col='grey',border=0) 

## top layer
plot(mapWorldAll, col = palette[varToPlot],border=F,add=T)


legend('left', legend = c("GREAT",'OK',"MEDIUM","BAD","LOST"), 
       fill = palette,
       cex = 0.6, 
       bty = "n",
       title="Clusters")
```




______

[GO BACK TO REPO](https://github.com/EvansDataScience/basicFinal_VISUAL)